C6\label{4.5 C8E Answer Key}
\subsection{Answer Key}
\tiny
\renewcommand{\insertclass}{- Class 8}
\renewcommand{\insertsubject}{ - English}

\begin{frame}[shrink=0.1,label=QPC8QC6E01 - DT - Q1]{Q1 [Interpretation Skill]}
\vspace{-0.2cm}

\mcqtextbottomOneFour{
questionnumber={1}, 
questionTag={C6E01 - DT - Q1}, 
questiontext={What does the word “frustrated” most likely mean in the sentence? \\
“He felt frustrated when the computer didn’t work”.
},
optionA={Happy},
optionB={Confused },
optionC={Angry },
optionD={Excited},
correctoption={C},
}


\begin{minipage}{\linewidth}
\hspace{1cm}
\centering
\tiny
\renewcommand{\arraystretch}{1.25}
\begin{tabular}{|M{1.2cm}|M{0.8cm}|M{0.8cm}|M{0.8cm}|M{0.8cm}|M{0.8cm}|}
\hline
Option & A (\ding{55}) & B (\ding{55}) & \cellcolor{cellgreen} C (\ding{51}) & D (\ding{55}) & E \\ 
\hline
8 A & \highno{8\%} & \highno{31\%} & \highno{54\%} & \highno{8\%} & \highno{0\%} \\ 
 \hline 
8 B & \highno{0\%} & \highno{47\%} & \highno{53\%} & \highno{0\%} & \highno{0\%} \\ \hline
\end{tabular}
\end{minipage}

\end{frame}
% \input{4. PPT/My Answer/English/C8/117_C8E - Q1}


\begin{frame}[shrink=0.1,label=QPC8QC6E01 - DT - P1 - Q1]{Q2 [Attention to Details]}
\vspace{-0.2cm}

\begin{minipage}{\textwidth}
\textbf{Read the passage and answer the following questions.} \\
\vspace{0.1cm}
Meera decided to bake a cake for her friend. She had flour, sugar, and butter at home, but no eggs. When she went to the store, she found eggs, sugar, chocolate, and vanilla syrup. She bought only the eggs and went home to complete the cake. When it was done, her friend loved the simple yet delicious cake. \\
\vspace{0.5cm}
\end{minipage}%  
\mcqtextbottomOneFour{
questionnumber={2}, 
questionTag={C6E01 - DT - P1 - Q1}, 
questiontext={Which ingredient was available both at Meera’s home and at the store?},
optionA={Flour},
optionB={Sugar },
optionC={Butter },
optionD={Vannila syrup},
correctoption={B},
}


\begin{minipage}{\linewidth}
\hspace{1cm}
\centering
\tiny
\renewcommand{\arraystretch}{1.25}
\begin{tabular}{|M{1.2cm}|M{0.8cm}|M{0.8cm}|M{0.8cm}|M{0.8cm}|M{0.8cm}|}
\hline
Option & A (\ding{55}) & \cellcolor{cellgreen} B (\ding{51}) & C (\ding{55}) & D (\ding{55}) & E \\ 
\hline
8 A & \highno{0\%} & \highgreen{92\%} & \highno{8\%} & \highno{0\%} & \highno{0\%} \\ 
 \hline 
8 B & \highno{0\%} & \highgreen{100\%} & \highno{0\%} & \highno{0\%} & \highno{0\%} \\ \hline
\end{tabular}
\end{minipage}

\end{frame}
% \input{4. PPT/My Answer/English/C8/117_C8E - Q2}


\begin{frame}[shrink=0.1,label=QPC8QC6E01 - DT - P1 - Q2]{Q3 [Understanding Skills]}
\vspace{-0.2cm}

\mcqtextbottomTwoTwo{
questionnumber={3}, 
questionTag={C6E01 - DT - P1 - Q2}, 
questiontext={Why did Meera go to the store?},
optionA={ To buy eggs for her friend},
optionB={To find more ingredients for her recipe},
optionC={To buy some decoration things},
optionD={To buy eggs for the cake},
correctoption={D},
}


\begin{minipage}{\linewidth}
\hspace{1cm}
\centering
\tiny
\renewcommand{\arraystretch}{1.25}
\begin{tabular}{|M{1.2cm}|M{0.8cm}|M{0.8cm}|M{0.8cm}|M{0.8cm}|M{0.8cm}|}
\hline
Option & A (\ding{55}) & B (\ding{55}) & C (\ding{55}) & \cellcolor{cellgreen} D (\ding{51}) & E \\ 
\hline
8 A & \highno{8\%} & \highno{8\%} & \highno{0\%} & \highgreen{85\%} & \highno{0\%} \\ 
 \hline 
8 B & \highno{13\%} & \highno{0\%} & \highno{0\%} & \highgreen{87\%} & \highno{0\%} \\ \hline
\end{tabular}
\end{minipage}

\end{frame}
% \input{4. PPT/My Answer/English/C8/117_C8E - Q3}


\begin{frame}[shrink=0.1,label=QPC8QC6E01 - DT - P1 - Q3]{Q4 [Analytical Skills]}
\vspace{-0.2cm}

\mcqtextbottomTwoTwo{
questionnumber={4}, 
questionTag={C6E01 - DT - P1 - Q3}, 
questiontext={ Why didn’t Meera buy chocolate or vanilla syrup?},
optionA={ She didn’t have enough money},
optionB={She didn’t require them for her cake},
optionC={She forgot to buy them},
optionD={Those items were out of stock at the store },
correctoption={B},
}


\begin{minipage}{\linewidth}
\hspace{1cm}
\centering
\tiny
\renewcommand{\arraystretch}{1.25}
\begin{tabular}{|M{1.2cm}|M{0.8cm}|M{0.8cm}|M{0.8cm}|M{0.8cm}|M{0.8cm}|}
\hline
Option & A (\ding{55}) & \cellcolor{cellgreen} B (\ding{51}) & C (\ding{55}) & D (\ding{55}) & E \\ 
\hline
8 A & \highno{8\%} & \highgreen{77\%} & \highno{15\%} & \highno{0\%} & \highno{0\%} \\ 
 \hline 
8 B & \highno{0\%} & \highgreen{100\%} & \highno{0\%} & \highno{0\%} & \highno{0\%} \\ \hline
\end{tabular}
\end{minipage}

\end{frame}
% \input{4. PPT/My Answer/English/C8/117_C8E - Q4}

%
\end{document}